02_DESeq_characterization

### 2019-08-27 analysis/03_DESeq2_characterization.Rmd
pheatmap working, but slow, only added 1 fig

```{r pca, eval = T}
FhypPCA <- returnPCAs(dds.female_hypothalamus)
FpitPCA <- returnPCAs(dds.female_pituitary)      
FgonPCA <- returnPCAs(dds.female_gonad)
MhypPCA <- returnPCAs(dds.male_hypothalamus)
MpitPCA <- returnPCAs(dds.male_pituitary)
MgonPCA <- returnPCAs(dds.male_gondad)

plotPC12(FhypPCA, "female hypothalamus")
plotPC12(FpitPCA, "female pituitary")
plotPC12(FgonPCA, "female gonad")
plotPC12(MhypPCA, "male hypothalamus")
plotPC12(MpitPCA, "male pituitary")
plotPC12(MgonPCA, "male gonad")
```

@@

```{r pheatmap, eval = F}
makepheatmap(dds.female_hypothalamus, "female hypothalamus")
makepheatmap(dds.female_pituitary, "female pituitary")
makepheatmap(dds.female_gonad, "female gonad")
makepheatmap(dds.male_hypothalamus, "male hypothalamus")
makepheatmap(dds.male_pituitary, "male pituitary")
makepheatmap(dds.male_gondad, "male gonad")
```
## plot candidate genes

>>>>

```{r pca, eval = T, cache = TRUE}

FhypPCA <- returnPCAs(dds.female_hypothalamus)
plotPC12(FhypPCA, "female hypothalamus")

FpitPCA <- returnPCAs(dds.female_pituitary)      
plotPC12(FpitPCA, "female pituitary")

FgonPCA <- returnPCAs(dds.female_gonad)
plotPC12(FgonPCA, "female gonad")

MhypPCA <- returnPCAs(dds.male_hypothalamus)
plotPC12(MhypPCA, "male hypothalamus")

MpitPCA <- returnPCAs(dds.male_pituitary)
plotPC12(MpitPCA, "male pituitary")

MgonPCA <- returnPCAs(dds.male_gondad)
plotPC12(MgonPCA, "male gonad")
```

@@

```{r pheatmap, eval = T, cache = TRUE}
colDataFH <- subsetcolData(c.colData, "female_hypothalamus")
#colDataFP <- subsetcolData(c.colData, "female_pituitary")
#colDataFG <- subsetcolData(c.colData, "female_gonad")
#colDataMH <- subsetcolData(c.colData, "male_hypothalamus")
#colDataMP <- subsetcolData(c.colData, "male_pituitary")
#colDataMG <- subsetcolData(c.colData, "male_gonad")

makepheatmap(dds.female_hypothalamus, colDataFH, "female hypothalamus")
#makepheatmap(dds.female_pituitary, colDataFP, "female pituitary")
#makepheatmap(dds.female_gonad, colDataFG, "female gonad")
#makepheatmap(dds.male_hypothalamus, colDataMH,  "male hypothalamus")
#makepheatmap(dds.male_pituitary, colDataMP, "male pituitary")
#makepheatmap(dds.male_gondad, colDataMG, "male gonad")
```
## plot candidate genes
